Bow shocks, bow waves, and dust waves. IV. Bow shape statistics

### 2019-04-22 papers/Papers1234/sec-quadrics-observations.tex
Start writing about LL bows for Paper IV

>>>>

We obtain a third sample of bow shocks from a catalog of stationary
emission line arcs in the Orion Nebula \citep{Bally:2000a}, which are
detected via their H\(\alpha\) emission in HST~ACS surveys of the nebula
\citep{Bally:2006a, Robberto:2013a}.  Out of a total of 73 such
objects \citep{Gutierrez-Soto:2015a} we have selected 18 where the
observations are of sufficient quality to reliably measure the
planitude and alatude.  Images in the ACS f658n filter of these
sources are shown in Figure~\ref{fig:ll-arcs}.  Some of the sources
were identified as LL~Orionis-type objects by \citet{Bally:2001a} and
are identified as LL~1--6. The remaining sources are labeled by their
coordinate-based designation according to the system of
\citet{ODell:1994a}.

In \S~7 of Paper~0, we discussed in detail 
Two of the sources, 000--400 and 069--641, were discussed in detail in
.
